\ripple: Differentiable and Hardware-Accelerated Waveforms for Gravitational Wave Data Analysis

### 2024-01-25 src/tex/ms.tex
updating showyourwork
typo correction

While we focused on \texttt{IMRPhenomD} here, the ability to apply AD to the calibration parameters may assist in other approaches to calibration, such as that used for the aligned-spin EOB model in~\citet{Bohe:2016gbl}.
Automative derivatives, if implemented for EOB waveforms, could allow for the application of other sampling methods such as HMC, or possibly optimization over the entire set of NR waveforms at once.

>>>>

While we focused on \texttt{IMRPhenomD} here, the ability to apply AD to the calibration parameters may assist in other approaches to calibration, such as that used for the aligned-spin EOB model in~\citet{Bohe:2016gbl}.
Automatic derivatives, if implemented for EOB waveforms, could allow for the application of other sampling methods such as HMC, or possibly optimization over the entire set of NR waveforms at once.
